Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-26 analysis/paper/paper.Rmd
Not using kableExtra
Remove from libraries in paper.Rmd
Update figures
Update with new N rate designators

library(bookdown)
library(kableExtra)
library(knitr)
library(ggpubr)
library(rice.awd.pests)
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Sheath Blight Incidence (%)") +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = PERC_TIL_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Tiller Sheath Blight Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = PERC_LEAF_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Leaf Sheath Blight Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

>>>>

library(bookdown)
library(knitr)
library(ggpubr)
library(rice.awd.pests)
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Sheath Blight Incidence (%)") +
  scale_shape_discrete(labels = c("N0",
                                  "N100",
                                  "N120",
                                  "N60",
                                  "N180")) +
  scale_linetype_discrete(labels = c("N0",
                                     "N100",
                                     "N120",
                                     "N60",
                                     "N180")) +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom")
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = PERC_TIL_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c("N0",
                                  "N100",
                                  "N120",
                                  "N60",
                                  "N180")) +
  scale_linetype_discrete(labels = c("N0",
                                     "N100",
                                     "N120",
                                     "N60",
                                     "N180")) +
  ylab("Tiller Sheath Blight Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom")
```

@@

ggplot(RAW_data,
       aes(x = DAI,
           y = PERC_LEAF_ShB,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_shape_discrete(labels = c("N0",
                                  "N100",
                                  "N120",
                                  "N60",
                                  "N180")) +
  scale_linetype_discrete(labels = c("N0",
                                     "N100",
                                     "N120",
                                     "N60",
                                     "N180")) +
  ylab("Leaf Sheath Blight Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom")
```
